---
title: "Deliverable 2"
author: "Scott Roes"
output:
  html_document:
    df_print: paged
---

I would like to predict if high scoring determines if you are on a good team or not. A lot of times there are players who score a lot but aren't on a good team. For many people including fans and scouts it will determine a lot about the player if he is not a good team or not. If that player is on a good team chances are that player has a great upside and potential. I will determine if high scoring means your are on a good team or not. I will do this through my second data source that stores the top 25 ranked teams in the nation and will use data from my first deliverable.
```{r}

include <- function(library_name){
  if( !(library_name %in% installed.packages()) )
    install.packages(library_name) 
  library(library_name, character.only=TRUE)
}
include("tidyverse")
include("knitr")
include("caret")
include("rvest")
include("dplyr")


purl("deliverable1.Rmd", output="part1.r")
source("part1.r")
```

Here is my second data source which includes the ranked teams. I obtained this data source via web scraping.
```{r}

rankings_web <- read_html("https://www.ncaa.com/rankings/basketball-men/d1/associated-press")

rank <- rankings_web %>%
  html_nodes("tbody") %>%
  html_nodes("tr")

Rank <- rank %>%
  html_nodes("td:first_child") %>%
  html_text() %>%
  as.integer()
Team <- rank %>%
  html_nodes("td:nth_child(2)") %>%
  html_text()
Points <- rank %>%
  html_nodes("td:nth_child(3)") %>%
  html_text()
Record <- rank %>%
  html_nodes("td:nth_child(4)") %>%
  html_text()

Rankings <- cbind.data.frame(Rank=Rank, Team=Team, Points=Points, Record=Record)

#tidying data
Rankings$Team <- gsub(" \\(48\\)", "", Rankings$Team)
Rankings$Team <- gsub(" \\(3\\)", "", Rankings$Team)
Rankings$Team <- gsub(" \\(9\\)", "", Rankings$Team)
Rankings$Team <- gsub(" \\(5\\)", "", Rankings$Team)


colnames(Rankings)[colnames(Rankings)=="Team"] <- "School"
colnames(Rankings)[colnames(Rankings)=="Points"] <- "Team_Points"
colnames(Rankings)[colnames(Rankings)=="Rank"] <- "Team_Rank"
colnames(Rankings)[colnames(Rankings)=="Record"] <- "Team_Record"

Rankings$Team_Points <- gsub(",", "", Rankings$Team_Points)
Rankings$Team_Points <- as.double(Rankings$Team_Points)


NCAAData <- merge(x=NCAAData, y=Rankings, by="School", all.x=TRUE)


```

Printing out NCAAData Table
```{r}

print(NCAAData)

```

Printing out Rankings Table
```{r}

print(Rankings)

```
To get a good idea here is a table of the Ranked teams and their total scoring I used from my second dataset.
```{r}
 
ggplot(data=Rankings, aes(x=Points)) +
  geom_jitter(aes(y=School, color=School))+
  labs(title="Top 25 Team Ranked Scoring", x="", y="") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```

Here I tried to use Points and other columns as an indicator to predict if high scoring determines how good the team is but I did not yield good results. However Rebounds gave me a good indicator to predict that good teams depend on rebounding. In order to use points as a good predictor I would need more paramaters or data.
```{r}
set.seed(385)
top25 <- filter(NCAAData, !is.na(NCAAData$Team_Points))
sample_selection <- top25$Team_Rank %>%
  createDataPartition(p=0.75, list=FALSE)
train <- top25[sample_selection, ]
test <- top25[-sample_selection, ]
train_model <- lm(Team_Rank ~ Minutes_Played + Points + Total_Rebounds + Assists + Steals + Field_Goal_Average, data=top25)
summary(train_model)
prediction <- train_model %>% predict(test)
R2(prediction, test$Team_Rank)

```
Here I found that that Win Shares per 40 minutes (the entire game time + if they win) is a good indicator to predict that good teams have decent win shares.
```{r}


train_model <- lm(Team_Rank ~ Total_Rebounds + Win_Shares_per40_Minutes, data=top25)
summary(train_model)
prediction <- train_model %>% predict(test)
R2(prediction, test$Team_Rank)


```




