author: "Scott Roes"
output:
  html_document:
    df_print: paged
---

I would like to predict if high scoring determines if you are on a ranked team or not. A lot of times there are players who score a lot but aren't on a ranked team. For many people including fans and scouts it will determine a lot about the player if he is not a ranked team or not. If that player is on a ranked team chances are that player has a great upside and potential. I will determine if high scoring means your are on a ranked team or not. I will do this through my second data source that stores the top 25 ranked teams in the nation and will use data from my first deliverable.
```{r}

include <- function(library_name){
  if( !(library_name %in% installed.packages()) )
    install.packages(library_name) 
  library(library_name, character.only=TRUE)
}
include("tidyverse")
include("knitr")
include("caret")
include("rvest")

#table from deliverable 1
NCAAData <- read_csv("https://raw.githubusercontent.com/TWanish/NBAPlayerValue/master/data/ncaaStats.csv")

# tidying data
colnames(NCAAData)[colnames(NCAAData) == "Pos"] <- "Position"
colnames(NCAAData)[colnames(NCAAData) == "G"] <- "Games"
colnames(NCAAData)[colnames(NCAAData) == "AST%"] <- "Assist_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "BLK%"] <- "Block_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "MP"] <- "Minutes_Played"
colnames(NCAAData)[colnames(NCAAData) == "FG"] <- "Field_Goal"
colnames(NCAAData)[colnames(NCAAData) == "FGA"] <- "Field_Goal_Average"
colnames(NCAAData)[colnames(NCAAData) == "FG%"] <- "Field_Goal_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "2P"] <- "Two_Pointers"
colnames(NCAAData)[colnames(NCAAData) == "2PA"] <- "Two_Point_Average"
colnames(NCAAData)[colnames(NCAAData) == "2P%"] <- "Two_Point_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "3P"] <- "Three_Pointers"
colnames(NCAAData)[colnames(NCAAData) == "3PA"] <- "Three_Point_Average"
colnames(NCAAData)[colnames(NCAAData) == "3P%"] <- "Three_Point_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "FT"] <- "Free_Throw"
colnames(NCAAData)[colnames(NCAAData) == "FTA"] <- "Free_Throw_Average"
colnames(NCAAData)[colnames(NCAAData) == "FT%"] <- "Free_Throw_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "TRB"] <- "Total_Rebounds"
colnames(NCAAData)[colnames(NCAAData) == "AST"] <- "Assists"
colnames(NCAAData)[colnames(NCAAData) == TL"] <- "Steals"
colnames(NCAAData)[colnames(NCAAData) == "BLK"] <- "Blocks"
colnames(NCAAData)[colnames(NCAAData) == "TOV"] <- "Turnovers"
colnames(NCAAData)[colnames(NCAAData) == "PF"] <- "Personal_Fouls"
colnames(NCAAData)[colnames(NCAAData) == "PTS"] <- "Points"
colnames(NCAAData)[colnames(NCAAData) == "ORtg"] <- "Offensive_Rating"
colnames(NCAAData)[colnames(NCAAData) == "DRtg"] <- "Defensive_Rating"
colnames(NCAAData)[colnames(NCAAData) == "PER"] <- "Player_Efficiency_Rating"
colnames(NCAAData)[colnames(NCAAData) == "TS%"] <- "True_Shooting_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "eFG%"] <- "Effective_Field_Goal_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "3PAr"] <- "Three_Pointer_Attempt_Rate"
colnames(NCAAData)[colnames(NCAAData) == "FTr"] <- "Free_Throw_Rate"
colnames(NCAAData)[colnames(NCAAData) == "PProd"] <- "Points_Produced"
colnames(NCAAData)[colnames(NCAAData) == "ORB%"] <- "Offensive_Rebound_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "DRB%"] <- "Defensive_Rebound_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "TRB%"] <- "Total_Rebound_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "STL%"] <- "Steal_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "TOV%"] <- "Turnover_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "USG%"] <- "Usage_Percentage"
colnames(NCAAData)[colnames(NCAAData) == "OWS"] <- "Offensive_Win_Shares"
colnames(NCAAData)[colnames(NCAAData) == "DWS"] <- "Defensive_Win_Shares"
colnames(NCAAData)[colnames(NCAAData) == "WS"] <- "Win_Shares"
colnames(NCAAData)[colnames(NCAAData) == "WS/40"] <- "Win_Shares_per40_Minutes"
colnames(NCAAData)[colnames(NCAAData) == "OBPM"] <- "Offensive_Box_Plus/Minus"
colnames(NCAAData)[colnames(NCAAData) == "DBPM"] <- "Defensive_Box_Plus/Minus"
colnames(NCAAData)[colnames(NCAAData) == "BPM"] <- "Box_Plus/Minus"


NCAAData <- filter(NCAAData, Player!="Cameron Curry")

```
Here is my second data source which includes the ranked teams. I obtained this data source via web scraping.
```{r}

rankings_web <- read_html("https://www.ncaa.com/rankings/basketball-men/d1/associated-press")

rank <- rankings_web %>%
  html_nodes("tbody") %>%
  html_nodes("tr")

Rank <- rank %>%
  html_nodes("td:first_child") %>%
  html_text() %>%
  as.integer()
Team <- rank %>%
  html_nodes("td:nth_child(2)") %>%
  html_text()
Points <- rank %>%
  html_nodes("td:nth_child(3)") %>%
  html_text()
Record <- rank %>%
  html_nodes("td:nth_child(4)") %>%
  html_text()

Rankings <- cbind.data.frame(Rank=Rank, Team=Team, Points=Points, Record=Record)

```
To get a good idea here is a table of the Ranked teams and their total scoring I used from my second dataset.
```{r}
 

filter(Rankings, Team %in% c('Louisville (48)', 'Kansas (3)', 'Maryland', 'Michigan (9)', 'Virginia (5)', 'Ohio State', 'North Carolina', 'Kentucky', 'Gonzaga', 'Duke', 'Michigan State', 'Arizona', 'Oregon', 'Auburn', 'Memphis', 'Seton Hall', 'Florida State', 'Baylor', 'Dayton', 'Colorado', 'Tennessee', 'Washington', 'Villanova', 'Butler', 'Utah State')) %>%
  ggplot(aes(x=Points)) +
  geom_jitter(aes(y=Team, color=Team)) + 
  labs(title="Top 25 Team Ranked Scoring", x="", y="") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```
Here are the top 25 ranked teams I used from my second dataset.
```{r}


 select(Rankings, Rank, Team)


```
Here I will show the players with the highest scoring along with their schools from my first dataset. Based on this view I tired to show the top scorers first but I wasnt able to write the correct syntax. With the correct syntax I would have shown a lot of high scoring players who were not on ranked teams. Then I would determine how many of those players were on ranked team and conclude that high scoring does not determine that you are on a ranked team. This is important becuase fans and scouts don't want to be fooled when a player who scores many points is not on a ranked team, meaning that certian player can be scoring high for reasons other than the team is good.
```{r}

 select(NCAAData, Player, Points, School)


```
